Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-05 paper.tex
small editorial comment tweaks

Cyclus was designed to operate natively in Unix/Linux type environments with
flexible and scriptable usage and input file format.  Cyclus stores its
comprehensive output data in a powerful open-source database format.  In addition
to information about material flows and facility deployments, Cyclus'
single-file database contains the simulation input file, version information
about the archetypes used in a simulation, the version of Cyclus used to run
the simulation, and the installed versions of Cyclus dependencies. This and
other features of Cyclus lend themselves well to automation, research
provenance and reproducibility, and large-scale computing.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\columnwidth]{exp2/sync-cycle.eps}
    \caption[The cycle staggering effect]{
        In this scenario, reactors are deployed annually with a refueling cycle
        length (including outage) of 18 months.  As a result, all reactors deployed
        every 3rd year refuel together.  All initial 100 LWRs start out with
        their cycles synced as well.
    }
    \label{fig:sync-cycle}
\end{figure}

>>>>

Cyclus was designed to operate natively in Unix/Linux type environments with
flexible and scriptable usage and input file format.  Cyclus stores its
comprehensive output data in a powerful open-source database format.  In addition
to information about material flows and facility deployments, Cyclus'
single-file database contains the simulation input file, version information
about the archetypes used in a simulation, the version of Cyclus used to run
the simulation, and the installed versions of Cyclus dependencies. This and
other features of Cyclus lend themselves well to automation, tracking research
provenance, reproducibility, and large-scale computing.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.0\columnwidth]{exp2/sync-cycle.eps}
    \caption[The cycle staggering effect]{
        In this scenario, reactors are deployed annually with a refueling cycle
        length (including outage) of 18 months.  As a result, all reactors deployed
        every 3rd year refuel together.  All initial 100 LWRs start out with
        their cycles synchronized as well.
    }
    \label{fig:sync-cycle}
\end{figure}
